---

title:  'Final Project'
subtitle: 'INFO 523'
author:
- name: Student -  [Michael Ayala]
  affiliation: [Student]
- name: Instructor -  Cristian Román-Palacios
  affiliation: School of Information, University of Arizona, Tucson, AZ
tags: [R, RStudio, HW3]
output: html_document

---

### Project Spcifications
association rules, price is a limiting fact, weighted association rules mining. 
kmean: clustering analysis 
independence, and be able to explain the information
walk through code and explain it in detail

Choosing specific housing parameters out of the data and determining what 
is the most abundant, affordable, and types of housing?

```{r}
#install.packages("tidyverse")
library('tidyverse')
#install.packages("readr")
library('readr')
library("scales")
library('arules')
library('arulesViz')
library('RColorBrewer')
library('cluster')
library('igraph')

```


```{r}
#Load Housing data from folder structure to dataset 
train <- read.csv("train.csv")
test <- read.csv("test.csv")

#House data variable select
 # Train has a sale price
h_trn <- train[, (colnames(train) %in%    
                    c('LotArea','FullBath','HalfBath','BsmtFullBath',
                      'HouseStyle','BedroomAbvGr','MSZoning','SalePrice'))]
 # Test does NOT have a sale price
h_tst <- test[, (colnames(test) %in%  
                    c('LotArea','FullBath','HalfBath','BsmtFullBath',
                      'HouseStyle','BedroomAbvGr','MSZoning','SalePrice'))]
```


```{r}
#  Test the Lost Size vs Sale Price 
Test1 <- ggplot(h_trn, aes(x=LotArea,y=SalePrice)) + geom_point() + theme_light() +
                    labs(title = 'Cost Per Lot Size',
                             x = 'Lot Area(sqr ft)',
                             y = 'Sale Price($)') +
                             scale_x_continuous(labels = comma_format(big.mark = ",")) + 
                             scale_y_continuous(labels = comma_format(big.mark = ","))
Test1

```

###MSZoning: Identifies the general zoning classification of the sale.
        A - Agriculture
        C - Commercial
       FV	- Floating Village Residential
        I	- Industrial
       RH	- Residential High Density
       RL	- Residential Low Density
       RP	- Residential Low Density Park 
       RM	- Residential Medium Density
       
```{r}
# The most abundant Zoning type must be determined 
Test2 <- ggplot(h_trn, aes(x=MSZoning,y=SalePrice)) + geom_point() + theme_light() + geom_jitter() +
                    labs(title = 'Cost vs Zone Type',
                             x = 'Zone Types',
                             y = 'Sale Price($)',) +
                             scale_y_continuous(labels = comma_format(big.mark = ","))
                            
Test2

```

###HouseStyle: Style of dwelling
       1Story	- One story
       1.5Fin	- One and one-half story: 2nd level finished
       1.5Unf	- One and one-half story: 2nd level unfinished
       2Story	- Two story
       2.5Fin	- Two and one-half story: 2nd level finished
       2.5Unf	- Two and one-half story: 2nd level unfinished
       SFoyer	- Split Foyer
         SLvl	- Split Level
       
```{r}
# The House Style that appears most  
Test3 <- ggplot(h_trn, aes(x=HouseStyle)) + geom_bar() + theme_light() +
                    labs(title = 'Availability of Specific House Style',
                             x = 'Styles of Houses',
                             y = 'Amount in Area')
Test3

```

```{r}
# Test the House Style 1 Story vs Lot Price 
Test4 <- ggplot(subset(h_trn,HouseStyle %in% '1Story'), aes(x=LotArea,y=SalePrice)) + geom_point() + theme_light() +
                    labs(title = 'Single Story - Cost Per Lot Size ',
                             x = 'Lot Area(sqr ft)',
                             y = 'Sale Price($)') +
                             scale_x_continuous(labels = comma_format(big.mark = ",")) + 
                             scale_y_continuous(labels = comma_format(big.mark = ","))
Test4
```

```{r}

# Filter Data 
F_Data <- filter(h_trn,LotArea < 50000 & MSZoning == 'RL' & HouseStyle =='1Story' & SalePrice < 600000)
Lot_Area_vs_Sale_Price <- F_Data[, (colnames(F_Data) %in% c('LotArea','SalePrice'))]

# Unsupervised Clustering of the Cost vs Lot Size based on Zoning and Single Story filtering 
model=kmeans(Lot_Area_vs_Sale_Price,5)
clusplot(Lot_Area_vs_Sale_Price,model$cluster)
clusplot(Lot_Area_vs_Sale_Price,model$cluster,color=T,shade=T)


```

#### 
BsmtFullBath: Basement full bathrooms
     Bedroom: Bedrooms above grade (does NOT include basement bedrooms)
    HalfBath: Half baths above grade
    FullBath: Full bathrooms above grade


```{r}
# More fine Filtering (Bathroom & Bedroom Situation )

Test6 <- h_trn[, (colnames(h_trn) %in% c('BsmtFullBath','FullBath','HalfBath','BedroomAbvGr'))]

ggplot(data = Test6,
       mapping = aes(x = BsmtFullBath, y = FullBath)) +
  geom_point() +
  facet_grid(rows = vars(HalfBath), cols =  vars(BedroomAbvGr)) + 
  labs(title = 'Bedrooms')

```

```{r}

# Filter Data 
R_Data <- filter(h_trn,LotArea < 50000 & 
                     MSZoning == 'RL' & 
                   HouseStyle =='1Story' & 
                     SalePrice < 600000 & 
                 BedroomAbvGr == 3 & 
                 BsmtFullBath == 1 & 
                     FullBath == 2 & 
                     HalfBath == 0)
Bed_vs_Bath_Filter_Lot_Area_vs_Sale_Price <- R_Data[, (colnames(R_Data) %in% c('LotArea','SalePrice'))]

# Unsupervised Clustering of the Cost vs Lot Size based on Zoning and Single Story filtering 
model=kmeans(Bed_vs_Bath_Filter_Lot_Area_vs_Sale_Price,5)
clusplot(Bed_vs_Bath_Filter_Lot_Area_vs_Sale_Price,model$cluster)
clusplot(Bed_vs_Bath_Filter_Lot_Area_vs_Sale_Price,model$cluster,color=T,shade=T)
```


```{r}

# The fitlered data without bathroom information is what we want to call out
# We noticed that the 1Story is the focus of this task 

T_Data <- train[, (colnames(train) %in%    
                    c('LotArea','FullBath','HalfBath','BsmtFullBath',
                      'HouseStyle','BedroomAbvGr','MSZoning','SalePrice'))]

set.seed(5)
appearance = list(default = "lhs", rhs = ("HouseStyle=1Story"))

#Support of 25% 
rules <- apriori(T_Data,parameter = list(supp = 0.25, conf = 0.1),appearance)

inspect(rules)

plot(rules,meausure=c("support","confidence"),shading = "lift")

plot(rules, method = "graph")

```

```{r}

#Support of 20% 
rules2 <- apriori(T_Data,parameter = list(supp = 0.20, conf = 0.1),appearance)

inspect(rules2)

plot(rules2,meausure=c("support","confidence"),shading = "lift")

plot(rules2, method = "graph")

```